---
output:
    html_notebook:
        toc: true
        toc_float: true
editor_options:
  chunk_output_type: inline
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(magrittr)
library(devtools)
```

# `rredlist` - package editor checks

## **Editor:** [\@]()

### Date:
**`r cat(sprintf("**Last updated:** %s", Sys.Date()))`**

***

<br>

This report documents the editor checks of **rOpenSci** submitted package:

### **`rredlist`: ropensci/software-review**  issue [\#NA](https://github.com/ropensci/onboarding/issues/).

<br>

## Package info

**Description:**

'IUCN' Red List (<https://api.iucnredlist.org/>) client.
    The 'IUCN' Red List is a global list of threatened and endangered species.
    Functions cover all of the Red List 'API' routes. An 'API' key is required.

**Author:** `r 
    c(person(given = "William",
             family = "Gearty",
             role = c("aut", "cre"),
             email = "willgearty@gmail.com"),
      person(given = "Scott",
             family = "Chamberlain",
             role = c("aut"),
             email = "myrmecocystus@gmail.com"),
      person(given = "rOpenSci",
             role = "fnd",
             comment = "https://ropensci.org/"),
      person(given = "Maëlle",
             family = "Salmon",
             role = "ctb",
             email = "maelle.salmon@yahoo.se")
      )`

**repo url:** <https://github.com/ropensci/rredlist>

**website url:** <https://docs.ropensci.org/rredlist>

## Review info


#### See [editors guidelines](https://ropensci.github.io/dev_guide/editorguide.html) for further information on the rOpenSci editors checks process.

**key editor checks:**



<!--Please be respectful and kind to the authors in your reviews. The rOpenSci [code of conduct](https://github.com/ropensci/onboarding/blob/master/policies.md/#code-of-conduct) is mandatory for everyone involved in our review process.-->


***

### session info


```{r sessionInfo}
sessionInfo()
```


```{r pkg_dir, echo = F}
pkg_dir <- "../rredlist"
```

## Test installation

### test local `rredlist` install:

```{r test-local}
install(pkg_dir, dependencies = T, build_vignettes = T)
```

```{r github-rm}
remove.packages("rredlist")
```
#### **comments:**

<!-- record comments on local install here -->

***

### test install of `rredlist` from GitHub with:

```{r test-github}
devtools::install_github("ropensci/rredlist", dependencies = T, build_vignettes = T)
```

#### **comments:**

<!-- record comments on github install here -->

***



## Check package integrity

### run checks on `rredlist` source:

```{r check-checks}
devtools::check(pkg_dir)
```
#### **comments:**

<!-- record comments on checks here -->

***

### run tests on `rredlist` source:

```{r check-tests}
devtools::test(pkg_dir)
```
#### **comments:**

<!-- record comments on tests here -->

***


### check `rredlist` for goodpractice:

```{r test-goodpractice}
goodpractice::gp(pkg_dir)
```
#### **comments:**

<!-- record comments on goodpractice here -->

***

## Check package metadata files

### inspect

- #### [README](https://github.com/ropensci/rredlist)
- #### [DESCRIPTION](https://github.com/ropensci/rredlist/blob/master/DESCRIPTION)

### spell check

```{r spell-check}
devtools::spell_check(pkg_dir)
```

#### **comments:**

<!-- record comments on metadata files here -->

***

## Review test suite:

### test coverage

```{r pkg_coverage}
covr::package_coverage(pkg_dir)

```

### inspect [tests](https://github.com/ropensci/rredlist/blob/master/tests/testthat)


#### **comments:**

<!-- record comments on testing suite here -->


***


### Reviewer assignment response:


ropensci, could you please add the rOpenSci under review badge to your README?
```
[![](https://badges.ropensci.org/NA_status.svg)](https://github.com/ropensci/software-review/issues/NA)
```

---

Reviewers:
Due date:

***



